---
title: "Clean-For-Model"
author: "Asmer Asrar Safi"
date: "5/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(fivethirtyeight)
library(tidyverse)
library(viridis)
library(transformr)
library(RColorBrewer)
library(readxl)
library(naniar)
library(dplyr)
library(readr)
library(markdown)
library(patchwork)
library(purrr)
library(stringr)
library(ggthemes)
library(tibble)
library(gganimate)
library(janitor)
library(skimr)
library(gt)
library(forcats)
library(jsonlite)
library(broom)
library(hrbrthemes)


```





# Error sources. Analyze (Less time period, only 18 countries, 2019 differences - India)

# 2019 data unavailable. 2012 - 2018 only. 


# twitter does not give us actual numbers of how many tweets and accounts were withheld 
# in every single request. thus only standardized variable we can use is percentage of requests 
# where some content was withheld on y - axis. 

#### This is my sample document. Here I test out my regressions before transferring them to the app. 


```{r}

# Cleaning Data for Modeling between GDP and the percentage where requests were withheld. Per year. 

# Reading the data 

twitter_gdp <- read_csv("twitter_gdp.csv")


twitter_gdp <- twitter_gdp %>% 
  
  # Creating the requests where some content was withheld variable by using the total_requests_made 
  # and percentage_where_some_conetent_withheld variables. Essentially, I want to change the percentage
  # to actual numbers. This will be crucial to find the total number of requests in each half (and then)
  # summing them to find what percentage of requests were complied to in the whole year.
  
  mutate(requests_where_content_withheld = (percentage_where_some_content_withheld*total_requests_made)/100) %>% 
  
  # Here I try to add the data to combine the different values of each half of the year
  # For example, I want to add the total requests where content was withheld in Jan-Jun 2016,
  # and Jul-Dec 2016 to find the total number of requests for the entire year. 
  
  group_by(year, country) %>% 
  
  mutate(sum_requests_where_content_withheld_yr = sum(requests_where_content_withheld)) %>% 
  
  mutate(sum_total_requests_made_yr = sum(total_requests_made)) %>% 
  
  ungroup() %>% 
  
  # Creating the percentage where some content withheld variable for each year 
  # based on the previous calculation. Now I'm done. 
  
  mutate(sum_percentage_where_content_withheld_yr = (sum_requests_where_content_withheld_yr/sum_total_requests_made_yr)*100) %>% 
  
  # Replacing NaN values with 0. 
  
  mutate(sum_percentage_where_content_withheld_yr = replace_na(sum_percentage_where_content_withheld_yr, 0)) %>% 
  
  # Rounding to 2 decimal places. 
  
  mutate(sum_percentage_where_content_withheld_yr = round(sum_percentage_where_content_withheld_yr, digits = 2)) %>% 
  
  select(country, year, sum_percentage_where_content_withheld_yr, gdp, sum_total_requests_made_yr) %>% 
  
  # Removing Venezuela. GDP data was unavailable.
  
  filter(!country == "Venezuela") %>% 
  mutate(year = as.double(year))
  
  
# Writing csv for app usage. 


write_csv(twitter_gdp, "twitter_gdp_modeling.csv")
```


```{r}

# Overall Country Plot + linear model. Code mostly the same as in the app. 
# Refer to app for more detailed comments on the plots/models. These are just
# rough tests. 

allcountries <- twitter_gdp %>%  
  
  ggplot(aes(gdp, sum_percentage_where_content_withheld_yr, size = sum_total_requests_made_yr)) +
  
  geom_point(alpha = 0.3,
            shape=21,
            color="black",
            fill="#69b3a2") +
  
  scale_x_log10() +
  
  geom_smooth(method = "lm", color = "dimgrey") +
  
  theme_minimal()


allcountries


  

allcountriesmodel <- 
  twitter_gdp %>%
  lm(sum_percentage_where_content_withheld_yr ~ gdp, data = .) %>% 
  tidy(conf.int = TRUE) %>% 
  select(Variable = term,
               Estimate = estimate,
               `Lower Bound` = conf.low,
               `Upper Bound` = conf.high)



allcountriesmodel


```


```{r}

# only those countries where at some point content was withheld (big 18)
# Code mostly the same as in the app. 
# Refer to app for more detailed comments on the plots/models. These are just
# rough tests. 

  
big18 <- twitter_gdp %>%  
  
  filter(country %in% c("Argentina",
                        "Australia",
                        "Belgium",
                        "Brazil",
                        "Canada",
                        "France",
                        "Germany",
                        "India",
                        "Ireland",
                        "Israel",
                        "Japan",
                        "Netherlands",
                        "New Zealand",
                        "Russia",
                        "South Korea",
                        "Spain",
                        "Turkey",
                        "United Kingdom")) 

```


```{r}

# big 18 and by year. Nothing's changed from the previous code except 
# from the fact that I also filter for the year. Pretty much the same. 


big18yr <- twitter_gdp %>%  
  
  filter(year == 2014) %>% 
  
  filter(country %in% c("Argentina",
                        "Australia",
                        "Belgium",
                        "Brazil",
                        "Canada",
                        "France",
                        "Germany",
                        "India",
                        "Ireland",
                        "Israel",
                        "Japan",
                        "Netherlands",
                        "New Zealand",
                        "Russia",
                        "South Korea",
                        "Spain",
                        "Turkey",
                        "United Kingdom")) %>%
  
  mutate(sum_percentage_where_content_withheld_yr = round(sum_percentage_where_content_withheld_yr, digits = 2)) %>% 
  
  ggplot(aes(gdp, sum_percentage_where_content_withheld_yr, size = sum_total_requests_made_yr)) +
  
   
  geom_point(alpha = 0.3,
            shape=21,
            color="black",
            fill="#69b3a2") +
  
  theme_minimal() +
  
  geom_smooth(method = "lm", color = "darkblue", se = FALSE) 


big18yr
```




```{r}

# Wrangling the Freedom + Twitter + GDP combined CSV i

freedom <- read_csv("freedom_twitter_gdp.csv")

# Creating the same variables in this data as in the previous one. Using an
# older version that I cleaned without the variables i needed, so thought 
# I'd just add them to this data set as opposed to cleaning the entire thing
# all over again, and writing a new csv. 

freedom <- freedom %>% 
  group_by(year, country) %>%
  mutate(sum_total_requests_made_yr = sum(total_requests_made)) %>% 
  mutate(sum_accounts_specified_yr = sum(accounts_specified)) %>% 
  select(country, region, year, sum_total_requests_made_yr, total_requests_made, freedom_score, sum_accounts_specified_yr)

write_csv(freedom, "freedom_twitter.csv")

```


